The zoon R package for reproducible and shareable species distribution modelling

### 2017-07-26 ms.Rmd
add link to website
add zenodo link to ms and readme

This module can now be shared so that others can use it in their zoon workflows.
Modules can be uploaded to the zoon modules repository via the online submission system at [URL TBD].
The zoon package vignette *Building modules* provides full details and examples of how to build modules of each type.

@@

Version 0.6 of the zoon R package is archived at https://doi.org/10.5281/zenodo.240926.
The code required to reproduce this manuscript can be downloaded at https://github.com/zoonproject/zoon_app_paper (to be replaced with zenodo archive link after proofing stage).

>>>>

This module can now be shared so that others can use it in their zoon workflows.
Modules can be uploaded to the zoon modules repository via the online submission system at [zoonproject.org](http://zoonproject.org).
The zoon package vignette *Building modules* provides full details and examples of how to build modules of each type.

@@

Version 0.6 of the zoon R package is archived at [doi.org/10.5281/zenodo.240926](https://doi.org/10.5281/zenodo.240926).
The code required to reproduce this manuscript is archived at [doi.org/10.5281/zenodo.834870](https://doi.org/10.5281/zenodo.834870).
